\section{Section 3: Professional vs. Ordinary Morality}
% Explain any conflict between professional and ordinary morality


The professional morality as guided by the ACM Code of Ethics in this case is quite clear. The ACM Code of Ethics values the betterment of society as a whole. Facilitating tax evasion does not improve society. Not only should the developer not include the feature, if the company chooses to have the software developed elsewhere, wherein the feature could be included the developer should report it. This can and should be reported anonymous to CRA, in accordance with the software developer’s professional morals. 
% Professional morality comes from ones professional code of ethics (ACM)
% Ordinary morality comes from one's chosen moral theory.
% Mention what moral values ground your ordinary morality


Ideally the software developer's ordinary morality would be in sync with their professional morality. However we are not aware of the developer's personal circumstances. Tax evasion is only beneficial to a small percentage of the population. The tax dollars spent by the government provide social programs to all or to those most vulnerable in society. It's likely that a developer working on an accounting software package and being ask to include this feature, would not benefit from it except for an immediate financial gain. At a federal level, Canada has a progressive tax system. Which means the more you money you earn, the more money you pay. Provincially, only Alberta with their flat 10\% tax rate does not follow a progressive tax system. This system is meant to provide equality and balance, and enable social programs that benifit all Canadians. So we would expect the software developer’s ordinary morality to guide them to refuse inclusion of the feature, and report the incident to the Canadian Revenue Agency or the authorities (RCMP).

% At this stage you should be talking about what your professional responsibilites say you should do in this case.
% And what your ordinary morality says you should do. 