\section{Section 2: Professional Responsibilies}
% Identify and explain the responsibilites and accountability that the agent has as an ACM professional
% 1.1 Contribute to society and human well-being. 1.2 Avoid harm to others. 
% 2.3 Know and respect existing laws pertaining to professional work.

In this case study, a software developer has been requested to include a feature that will likely be used to facilitate breaking the law. In these circumstances the CRA will go after the users of the software, and the provider and creators of the software all the same. Providing a means to evade taxes is not only illegal, but the unpaid tax dollars would have been spent providing society with services. Which is why providing the requested feature would contradict the ACM code of ethics: ``1.1 Contribute to society and human well-being'' (ACM Code of Ethics, p. 91). A large portion of taxes collected by the CRA is distributed by the federal government to the provinces in the form of transfer payments. The taxes are then spent providing services such as education and healthcare. 

Including this software feature would put the developer and the company for which they work at risk legally. The repercussions of getting caught by the CRA would be devastating. The developer could go to prison; which would hurt any family member's they support. The software firm for which the developer worked, would face both legal and public relation consequences. These would likely destroy the company, and if the developer was in house, the company would be exposed and face extreme penalties. This pertains to ``1.2 Avoid harm to others'' (ACM Code of Ethics, p. 91) because there are many others with jobs and careers at steak.

Knowing the laws and penalties around taxation when asked to write an accounting program is important. The developer should know that Tax Avoidance is generally legal, while Tax Evasion is always illegal in Canada. There can be arguments over what is avoiding taxation and what is evading taxation, but in this case it is clear. The feature requested would hide accounts, which would automatically be considered tax evasion if discovered. Canada Revenue Agency administers a self-assessment system, which relies on taxpayers to report their own earnings and pay their fair share. Taxpayers are allowed to minimize the amount of taxes they must pay, but not allowed to hide assets or earnings to try to pay less. The developer should ``2.3 Know and respect existing laws pertaining to professional work.'' (ACM Code of Ethics, p. 94)  
% Can also use parts of the the IEEE ethics%
% Should primarily use ACM ethics