\begin{abstract}
In this case study, we examane ``Case: 4 Taxation:'' 
\begin{quote}
``You are writing an accounting program. The person that wants it asks you to add some features 
to hide some accounts from the Canada Revenue Agency. What should you do?''
\end{quote}
\end{abstract}

\section{Section 1}
% Pick a situation from the list of cases.

% Identify and describe in your own words the ethical issues of the situation.
In this case study, ``Taxation'' we have 5 moral entities. The essence of the case revolves around a moral agent who is writing software for ``the person'' being asked to include a feature that will likely be used to break the law. We shall refer to ``the person'' as the client, who is paying for the services of the developer. The feature being requested, will aid the end users in tax avoidance and tax evasion. Tax Avoidance is generally illegal and Tax Evasion is illegal in Canada. This is in accordance with the Income Tax Act, it is the Canadian Revenue Agency who collects from and inspects taxpayers. The feature requested will not only increase the difficult job of the CRA, it will also enable stealing from the fifth and final moral entity, Canadians. Tax Evasion is robbing from the federal government, which is robbing from the people of Canada.
% Includes identifying the moral parties


If the developer complies with their client's request, it will enable the end users to hide assets from the CRA. Hiding assets from the CRA is stealing from the federal government. That money would have been used to provide services for Canadian residents and citizens. When the CRA discovers the developer has aided in tax avoidance and tax evasion, they will press criminal charges. If the CRA does not catch on, the developer’s reputation could spread as someone who endorses ethically questionable software. This would be an attraction for unsavoury clients, and could result in more illegal requests. The legal system should catch this eventually, and the developer would lose everything.  
% ALL moral entities, not just the people who act but also those affected.


If the developer opts to refuse including the requested features, they will likely lose the contract with their client. We do not have any information about the size of the organization for which the developer works. Is the developer part of a larger software firm? Are there others who will lose money or jobs? Is this client a major business asset? Is the developer employed directly by the client as an in-house developer? In which case the client is their boss.
% Be sure to include the consequences of an agent's action
% Remember: you are describing the moral aspects and the ethical issues not retelling the story to reader