\section{Section 4: Conclusion}
% Articulate your final moral analysis of the situation
Ultimately the software developer should refuse to include the account hiding feature being requested. There are many things at risk such as the developer's career and the credibility of the firm for which they work. The penalties surrounding tax evasion would not simply tarnish one's reputation, they would ruin the developer's livelihood and likely place the developer behind bars alongside those who actually attempted to evade taxation. If the company goes to competition to have their software developed, this should be reported to the CRA. The CRA takes tax evasion seriously and continually investigates and reviews tax avoidance schemes. 
% That is, explain what you should ultimately do in the situation you have chosen..

Agreeing to include the software feature would put the developer at risk personally, and would only benefit a small percentage of the Canadian population. This contradicts the rights and responsibilites that come with Canadian citizenship, and it would be against the ACM Code of Ethics. Canadian citizenship comes with responsibilites as layed out in the Canadian Charter of Rights and Freedoms, two of which are "Obeying the law" and "Helping others in the community" (Discover Canada, p. 9). Every Canadian citizen can contribute to the improvement and progress of society as a whole, this is why the request for the software feature should be declined. 
% In giving the explanation you must give reasons for why you think you should act a certian way.